Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-09-23 paper/lncsFormat.tex
add hood graph
before third revision

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\maketitle

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading. 
The following contributions are made in \textsc{LTDetector}.
(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs. 
(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。

@@

Knowledge base can be a good supplementary for event detection on microblog stream.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``libyan rebel chief gunned down in Benghazi (2011-07-28)'' is short, but still comprehensible because the words ``\textit{libyan}", ``\textit{Benghazi}'' are included in the wiki page ``\textit{Libya}", and the words ``\textit{rebel}'', ``\textit{gun}'' appeared in the wiki page ``\textit{Military}''.
By reading these two wiki pages, readers easily understand the example tweet is talking about something related to \textit{Military} and \textit{Libya}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.

@@

In our paper, to balance the performance and the cost of transfer learning, new data structure \textit{history states} is proposed. 
It bases on the following facts. 
The knowledge base's three fold structure includes the taxonomy graph (\textit{class} \(\rightarrow\) \textit{subclass}), the category-page bipartite graph (\textit{class} \(\rightarrow\) \textit{instance}), and the page-content map (\textit{instance} \(\rightarrow\) \textit{content}) relations in the knowledge base. 
In terms of concept level, the latter part is finer than the former. 
And the last page-content map goes into the detail at the word level. 
By considering these three parts together, we can extract a class or category's highly related words (evaluated by chi-square score in Section \ref{subsec:hs_initialization}), and restore them in the newly proposed data structure \textit{history states}.
In transfer learning, \textit{history states} play an important role at speeding up building the linkage between the word in microblog and the high level concept in knowledge base.

More than that, we propose a new quick and lightweight probabilistic model \textsc{HS-Prior-LDA} for transfer learning. 
After deriving \textsc{HS-Prior-LDA} (detailed in Section \ref{subsec:rs_initialization}), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{history state}, the linkages of microblogs' other words, the linkages of the word types in the same time window. 
All these statistics are easy to gain, which leads the model efficient. 
What \textsc{HS-Prior-LDA} learned is summarized as \textit{recent states}, shown in Figure \ref{fig:modelDesc}.
Since the recent states have filtered out meaningless words, the detected events on recent states is much more accurate than other methods which don't do the transfer learning.
\textsc{HS-Prior-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
Our experiment on the real dataset \textit{Edinburgh twitter corpus (30 million tweets)} validates the effectiveness of our proposed method \textsc{LTDetector}.

>>>>

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
\maketitle

\begin{abstract}
Many web applications need the accurate event detection technique on microblog stream. 
But the accuracy of existing methods are still challenged by microblog's short length and high noise. 
We develop a novel lightweight transfer learning method \textsc{LTDetector} to deal with the task.  
\textsc{LTDetector} bases on two facts, that microblog is short but can be enriched by knowledge base semantically with transfer learning; and to make the transfer efficiently and effectively, the scale of knowledge should shrink without degrading. 
The following contributions are made in \textsc{LTDetector}.
%我们的核心贡献应该是说，我们提出了一个方法（结构Guided的词表抽取方法），用这个方法可以从维基中学习出来了一个高度准确的词表，这个词表对于迁移学习非常有效。
(1) We formalize the knowledge base's hierarchical structure into three parts including taxonomy graph, category-page bipartite graph, and page-content map; and further shrink the scale of knowledge to category-word level by utilizing the structure.
%结构提取的方法(without degrading)
Specifically, category's highly related words and their chi-square scores, namely category's \textit{KB State}, are condensed.
%The knowledge base's hierarchical structure is formalized as three-part: taxonomy graph, category-page bipartite graph, and page-content map.
%The structure is utilized to condense category's highly related words and their chi-square scores, namely category's \textit{KB State}, shrinking the scale of knowledge to category-word level.
(2) Category's related words in microblog stream, namely category's \textit{Stream State}, are learned from our proposed KB-Prior-LDA, which exploits the word co-occurrences and transfers the condensed knowledge \textit{KB State} into microblogs. 
%基于结构提取方法的迁移学习，学习到microblog的状态
(3) Events are further detected on meaningful categories' \textit{Stream States}, which filter out the noise accurately. 
(4) Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed transfer learning method.
\textsc{LTDetector} achieves high accuracy, promoting the precision by 9\% without  sacrificing the recall rate.
%另外，我们还标注了事件，使其语义可理解。以及LTDetector是efficient的。

@@

Knowledge base can be a good supplementary for event detection on microblog stream.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``Possible Ft. Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft. Hood}" is included in the wiki page ``\textit{Ft. Hood}", and belongs to the category ``\textit{Military}''.
By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
%拆成两个小图，中间说明这是transfer learning过后的
\begin{figure}[h]
        \centering
        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
        \caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
        \label{fig:hood}
\end{figure}

@@

In our paper, to balance the performance and the cost of transfer learning, new data structure \textit{KB states} is proposed. 
It bases on the following facts. 
The knowledge base's three fold structure includes the taxonomy graph (\textit{class} \(\rightarrow\) \textit{subclass}), the category-page bipartite graph (\textit{class} \(\rightarrow\) \textit{instance}), and the page-content map (\textit{instance} \(\rightarrow\) \textit{content}) relations in the knowledge base. 
In terms of concept level, the latter part is finer than the former. 
And the last page-content map goes into the detail at the word level. 
By considering these three parts together, we can extract a class or category's highly related words (evaluated by chi-square score in Section \ref{subsec:hs_initialization}), and restore them in the newly proposed data structure \textit{history states}.
In transfer learning, \textit{history states} play an important role at speeding up building the linkage between the word in microblog and the high level concept in knowledge base.

More than that, we propose a new quick and lightweight probabilistic model KB-Prior-LDA for transfer learning. 
After deriving KB-Prior-LDA (detailed in Section \ref{subsec:rs_initialization}), it reveals that whether a word in microblog links to a high-level category in knowledge base depends on three factors, the word's score in the category's \textit{KB state}, the linkages of microblogs' other words, the linkages of the word types in the same time window. 
All these statistics are easy to gain, which leads the model efficient. 
What KB-Prior-LDA learned is summarized as \textit{recent states}, shown in Figure \ref{fig:modelDesc}.
Since the recent states have filtered out meaningless words, the detected events on recent states is much more accurate than other methods which don't do the transfer learning.
\textsc{KB-Prior-LDA}, \textit{history states}, and \textit{recent states} forms up our proposed event detection method \textsc{LTDetector}.
Our experiment on the real dataset \textit{Edinburgh twitter corpus (30 million tweets)} validates the effectiveness of our proposed method \textsc{LTDetector}.
